The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-10-25 Paper_Analyses.tex
update 24.10.2018
better model interpretation
vocabulary summary
choosing figures to include

\begin{tabular}{l|r|r}
\hline
Publication Type & \# Items & \# Effect Sizes\\
\hline
dissertation & 2 & 17\\
\hline
gray paper & 2 & 14\\
\hline
paper & 27 & 216\\
\hline
proceedings & 1 & 4\\
\hline
\end{tabular}

@@

\begin{tabular}{l|r|r}
\hline
Type of comparison & \# Papers & \# Effect Size\\
\hline
post-naming compared to pre-naming phase & 10 & 29\\
\hline
post-naming phase compared with chance (=50\%) & 9 & 23\\
\hline
post-pre difference score compared with chance (=0) & 13 & 52\\
\hline
\end{tabular}

@@

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 25) or using reported
t-values (\emph{n} = 9). Raw means and standard deviations were
extracted from figures for 3 papers. In a within-participation design,
when two means are compared (i.e.~looking during pre- and post-naming)
it is necessary to obtain correlations between the two measurements at
the participant level to calculate effect sizes and effect size variance
based on t-values. Upon request we were provided with correlation values
for one paper (Altvater-Mackensen, 2010); we were able to compute
correlations using means, standard deviations, and t-values for \emph{n}
= 4 (following Csibra, et al. 2016, Appendix B; see also Rabagliati,
Ferguson, \& Lew-Williams, 2018). Correlations were imputed for the
remaining papers (see Black \& Bergmann, 2017, for the same procedure).
We could compute a total of 104 effect sizes for correct pronunciations
and 147 for mispronunciations.

@@

{[}CHRISTINA: Do you think we have to revise this section? I think it's
the same as in the proceedings paper.{]}{[}KATIE: Are you concerned
about the Publication Bias section in particular, or the Methods as a
whole? In general, some of the Methods was written before the CogSci
paper and in other places to flesh things out I rewrote what we had. Its
definitely giving the same information and sometimes the wording is
close, because there's not too many different ways to explain what a
funnel plot is :){]}

@@

{[}CHRISTINA: Let's both reread the full paper once it is ready and
check that this is properly motivated and whether we do need to list
them all. For now I think the last sentence is fine, but I would tend to
prefer a reminder for the forgetful reader.{]}{[}KATIE: that's
reasonable! We had just listed everything 7 paragraphs before, which
doesn't seem like a lot of \enquote{space}.{]}

@@

{[}CHRISTINA: If we want to interpret here, how about the next
bit.{]}{[}KATIE: YES! This is an excellent point!!!{]}

@@

{[}CHRISTINA: CAn you add the stats for the non-sig results?{]}{[}KATIE:
Are there stats that can be computed on the non-sig results? Or do you
just want an n for significant and non-significant studies?{]}

@@

We first calculated the meta-analytic effect for object identification,
i.e.~looks to the target image in response to correctly pronounced
words. The variance-weighted meta-analytic effect size Hedges' \emph{g}
was 0.91 (SE = 0.12) which was significantly different from zero (95\%
CI {[}0.67, 1.14{]}, \emph{p} \textless{} .001). This is a rather large
effect size (according to the criteria set by Cohen, 1988; see also
Bergmann, et al., 2018; for comparative meta-analytic effect sizes in
language acquisition research). That the effect size is significantly
above zero suggests that when presented with the correctly pronounced
label, infants fixated the corresponding object. Our analysis of funnel
plot asymmetry, however, found evidence for publication bias, which
might lead to an overestimated effect sizes as smaller, non-significant
results might not be published. Although the effect size Hedges'
\emph{g} may be overestimated for object identification in response to
correctly pronounced words, the p-curve results and a CI lower bound of
0.67 suggests that this result is robust even when correcting for
publication bias. In other words, we are confident that the true
population mean lies above zero for object recognition of correctly
pronounced words.

{[}CHRISTINA: Can you explain what the CI lower bound means here? I
don't follow.{]}{[}KATIE: What do you think about this? The CI lower
bound stuff here actually comes from something you wrote, so tell me
whether its correct.{]}

We then calculated the meta-analytic effect for object identification in
response to mispronounced words. In this case, the variance-weighted
meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
was also significantly different from zero (95\% CI {[}0.13, 0.37{]},
\emph{p} \textless{} .001). This is considered a small effect size
(Cohen, 1988), but significantly above zero, which suggests that even
when presented with a mispronounced label, infants fixated the correct
object. In other words, infants are able to resolve mispronunciations, a
key skill in language processing We again note the publication bias
(which was smaller in this condition), and the possibility that the
effect size Hedges' \emph{g} may be overestimated. But, as the p-curve
indicated evidential value, we are confident in the overall patterns,
namely that infants fixate the target even after hearing a mispronounced
label.

@@

The above two analyses considered the data from mispronounced and
correctly pronounced words separately. To evaluate mispronunciation
sensitivity, we compared the effect size Hedges' \emph{g} for correct
pronunciations with mispronunciations directly, merging the two
datasets. The moderator test was significant, QM(1) = 215.76, \emph{p}
\textless{} .001. Hedges' \emph{g} for mispronunciation sensitivity was
0.50 (SE = 0.03), which indicated that the responses across conditions
were significantly different (95\% CI {[}0.43, 0.56{]}, \emph{p}
\textless{} .001). This confirms that although infants fixate the
correct object for both correct pronunciations and mispronunciations,
the observed fixations to target (as measured by the effect sizes) were
significantly greater for correct pronunciations. In other words, we
observe a significant difference between the two conditions and can now
quantify the modulation of fixation behavior in terms of standardized
effect sizes.

@@

To evaluate the different predictions we laid out in the introduction
for how mispronunciation sensitivity will change as infants develop, we
next added the moderator age (centered, in days). In the first analyses,
we investigate the impact of age separately on conditions where words
were either pronounced correctly or not. Age did not significantly
modulate object identification in response to correctly pronounced
(QM(1) = 0.68, \emph{p} = 0.41) or mispronounced words (QM(1) = 1.72,
\emph{p} = 0.19). The lack of a significant modulation together with the
small estimates indicates that there was no relationship between age and
target looks in response to a correctly pronounced or mispronounced
label. This relationship is plotted in Figure 2.

{[}CHRISTINA{]} CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere
where you report a p-value {[}KATIE: Do you know how to calculate
Estimates and CIs for the Test of Moderators? Or do you mean reporting
the estimates and CIs even when the moderator test is not
significant?{]}

We then examined the interaction between age and mispronunciation
sensitivity (correct vs.~mispronounced words) in our whole dataset. The
moderator test was significant (QM(3) = 218.62, \emph{p} \textless{}
.001). This result is in line with the general observation that as
infants mature they become better at language processing. The
interaction between age and mispronunciation sensitivity, however, was
not significant \(\beta\) = 0.00, (SE = 0.01, 95\% CI {[}-0.01, 0.02{]},
\emph{p} = 0.731), suggesting that as infants age, their
mispronunciation sensitivity remains the same.

@@

Of the 32 papers included in the meta-analysis, 8 (comprehension = 7
papers; production = 1) analyzed the relationship between vocabulary
scores and mispronunciation sensitivity. There is reason to believe that
production data are different from comprehension data (the former being
easier to estimate for parents in the typical questionnaire-based
assessment), so we analyze this data separately.

{[}KATIE{]} I DON'T KNOW HOW TO INTERPRET THESE RESULTS\ldots{} THE
FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT
MEANINGFUL? {[}CHRISTINA{]} SO WE DON'T WANT TO INTERPRET THE FIXED
EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE
BETWEEN EVERY RECORD (LANGUAGE ETC). I WOULD INTERPRET THE OVERALL
CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER
WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY
MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION
COEFFICIENTS CONSISTENYL BELOW .1 WE THEREFORE MUST CONCLUDE THAT WITHIN
NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE
CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE
NECESSARY RAW DATA. {[}KATIE: Ah, so because for each paper the
correlation and CI values straddle 0, this indicates that there really
isn't much evidence for a relationship? I think it could make sense to
add this to supplementary materials. Over the summer, I had also played
around with looking at how collection of vocabulary data has dropped off
over the years, even though more mispronunciation studies have been
published. That might be something interesting to add. If we truly think
that this is what is driving the development of mispronunciation
sensitivity, then why are people not collecting this data?{]} (BUT I
WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE
CORRELATION AND THEN DO SOMETHING WITH THAT?) {[}KATIE: I'm not really
sure what you mean by this :({]}

\begin{verbatim}
##                                      COR            95%-CI %W(fixed)
## Zesiger et al. (2012)             0.0610 [-0.3553; 0.4773]       5.8
## Zesiger et al. (2012)            -0.1590 [-0.5663; 0.2483]       6.1
## Mani, Coleman, & Plunkett (2008)  0.0300 [-0.2271; 0.2871]      15.2
## Swingley & Aslin (2000)           0.1050 [-0.1564; 0.3664]      14.7
## Mani & Plunkett 2007             -0.1700 [-0.5234; 0.1834]       8.0
## Mani & Plunkett 2007             -0.1700 [-0.5175; 0.1775]       8.3
## Swingley & Aslin (2002)           0.1410 [-0.2432; 0.5252]       6.8
## Swingley & Aslin (2002)           0.1410 [-0.2596; 0.5416]       6.3
## Swingley 2003                     0.3400 [ 0.0470; 0.6330]      11.7
## Swingley 2003                     0.0600 [-0.3472; 0.4672]       6.1
## Hojen et al.                      0.2220 [-0.2591; 0.7031]       4.3
## Hojen et al.                      0.4820 [ 0.0935; 0.8705]       6.7
##                                  %W(random)
## Zesiger et al. (2012)                   6.2
## Zesiger et al. (2012)                   6.5
## Mani, Coleman, & Plunkett (2008)       13.7
## Swingley & Aslin (2000)                13.4
## Mani & Plunkett 2007                    8.3
## Mani & Plunkett 2007                    8.5
## Swingley & Aslin (2002)                 7.2
## Swingley & Aslin (2002)                 6.7
## Swingley 2003                          11.2
## Swingley 2003                           6.5
## Hojen et al.                            4.8
## Hojen et al.                            7.0
## 
## Number of studies combined: k = 12
## 
##                         COR            95%-CI    z p-value
## Fixed effect model   0.0897 [-0.0105; 0.1900] 1.75  0.0795
## Random effects model 0.0893 [-0.0212; 0.1999] 1.58  0.1132
## 
## Quantifying heterogeneity:
## tau^2 = 0.0060; H = 1.09 [1.00; 1.50]; I^2 = 15.7% [0.0%; 55.4%]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  13.05   11  0.2899
## 
## Details on meta-analytical method:
## - Inverse variance method
## - DerSimonian-Laird estimator for tau^2
## - Untransformed correlations
\end{verbatim}

\begin{verbatim}
##                                      COR            95%-CI %W(fixed)
## Zesiger et al. (2012)            -0.0090 [-0.4268; 0.4088]       5.0
## Zesiger et al. (2012)            -0.1720 [-0.5775; 0.2335]       5.3
## Mani, Coleman, & Plunkett (2008)  0.0700 [-0.1861; 0.3261]      13.2
## Mani & Plunkett 2007             -0.1100 [-0.4696; 0.2496]       6.7
## Mani & Plunkett 2007             -0.1100 [-0.4635; 0.2435]       6.9
## Swingley & Aslin (2002)           0.1820 [-0.1970; 0.5610]       6.0
## Swingley & Aslin (2002)           0.1820 [-0.2131; 0.5771]       5.6
## Swingley 2003                     0.1800 [-0.1406; 0.5006]       8.4
## Swingley 2003                     0.0700 [-0.3367; 0.4767]       5.2
## Ramon-Casas et al. 2009           0.0980 [-0.3068; 0.5028]       5.3
## Ramon-Casas et al. 2009          -0.1470 [-0.5468; 0.2528]       5.4
## Ramon-Casas et al. 2009          -0.2300 [-0.6171; 0.1571]       5.8
## Ramon-Casas et al. 2009           0.2400 [-0.1451; 0.6251]       5.9
## Ramon-Casas et al. 2009           0.4350 [ 0.1037; 0.7663]       7.9
## Hojen et al.                      0.2220 [-0.2591; 0.7031]       3.7
## Hojen et al.                     -0.1480 [-0.6430; 0.3470]       3.5
##                                  %W(random)
## Zesiger et al. (2012)                   5.0
## Zesiger et al. (2012)                   5.3
## Mani, Coleman, & Plunkett (2008)       13.2
## Mani & Plunkett 2007                    6.7
## Mani & Plunkett 2007                    6.9
## Swingley & Aslin (2002)                 6.0
## Swingley & Aslin (2002)                 5.6
## Swingley 2003                           8.4
## Swingley 2003                           5.2
## Ramon-Casas et al. 2009                 5.3
## Ramon-Casas et al. 2009                 5.4
## Ramon-Casas et al. 2009                 5.8
## Ramon-Casas et al. 2009                 5.9
## Ramon-Casas et al. 2009                 7.9
## Hojen et al.                            3.7
## Hojen et al.                            3.5
## 
## Number of studies combined: k = 16
## 
##                         COR            95%-CI    z p-value
## Fixed effect model   0.0601 [-0.0331; 0.1533] 1.26  0.2061
## Random effects model 0.0601 [-0.0331; 0.1533] 1.26  0.2061
## 
## Quantifying heterogeneity:
## tau^2 = 0; H = 1.00 [1.00; 1.42]; I^2 = 0.0% [0.0%; 50.7%]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  14.51   15  0.4870
## 
## Details on meta-analytical method:
## - Inverse variance method
## - DerSimonian-Laird estimator for tau^2
## - Untransformed correlations
\end{verbatim}

\begin{verbatim}
##                              COR             95%-CI %W(fixed) %W(random)
## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
## Swingley (2009)          -0.1200 [-0.3715;  0.1315]       6.4        5.6
## Swingley (2009)           0.1300 [-0.1957;  0.4557]       3.8        3.8
## Swingley & Aslin (2000)   0.4210 [ 0.2036;  0.6384]       8.6        6.7
## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
## Mani & Plunkett 2007     -0.1700 [-0.5234;  0.1834]       3.3        3.3
## Mani & Plunkett 2007     -0.1700 [-0.5175;  0.1775]       3.4        3.4
## Mani & Plunkett 2007      0.1000 [-0.2667;  0.4667]       3.0        3.2
## Mani & Plunkett 2007     -0.2800 [-0.6214;  0.0614]       3.5        3.5
## Mani & Plunkett 2007     -0.0700 [-0.3354;  0.1954]       5.8        5.2
## Mani & Plunkett 2007      0.1000 [-0.1641;  0.3641]       5.8        5.2
## Swingley & Aslin (2002)   0.1750 [-0.2050;  0.5550]       2.8        3.0
## Swingley & Aslin (2002)   0.1750 [-0.2212;  0.5712]       2.6        2.8
## Mani & Plunkett 2010     -0.3500 [-0.6640; -0.0360]       4.1        4.0
## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
## Hojen et al.             -0.0510 [-0.5557;  0.4537]       1.6        1.8
## Hojen et al.              0.0510 [-0.4537;  0.5557]       1.6        1.8
## Hojen et al.              0.0600 [-0.4442;  0.5642]       1.6        1.8
## Hojen et al.             -0.0600 [-0.5642;  0.4442]       1.6        1.8
## Tao et al. 2012           0.5700 [ 0.1710;  0.9690]       2.6        2.7
## 
## Number of studies combined: k = 31
## 
##                         COR            95%-CI    z p-value
## Fixed effect model   0.0377 [-0.0260; 0.1014] 1.16  0.2465
## Random effects model 0.0322 [-0.0399; 0.1043] 0.87  0.3818
## 
## Quantifying heterogeneity:
## tau^2 = 0.0079; H = 1.11 [1.00; 1.39]; I^2 = 19.3% [0.0%; 48.4%]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  37.18   30  0.1719
## 
## Details on meta-analytical method:
## - Inverse variance method
## - DerSimonian-Laird estimator for tau^2
## - Untransformed correlations
\end{verbatim}

\begin{verbatim}
##                             COR             95%-CI %W(fixed) %W(random)
## Swingley (2009)          0.0700 [-0.1839;  0.3239]       6.4        5.4
## Swingley (2009)          0.1600 [-0.1628;  0.4828]       3.9        3.8
## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
## Mani & Plunkett 2007    -0.1100 [-0.4696;  0.2496]       3.2        3.3
## Mani & Plunkett 2007    -0.1100 [-0.4635;  0.2435]       3.3        3.3
## Mani & Plunkett 2007     0.2300 [-0.1208;  0.5808]       3.3        3.4
## Mani & Plunkett 2007     0.2200 [-0.1325;  0.5725]       3.3        3.4
## Mani & Plunkett 2007    -0.2700 [-0.5173; -0.0227]       6.7        5.5
## Mani & Plunkett 2007    -0.0590 [-0.3248;  0.2068]       5.8        5.0
## Swingley & Aslin (2002)  0.0290 [-0.3627;  0.4207]       2.7        2.8
## Swingley & Aslin (2002)  0.0290 [-0.3793;  0.4373]       2.5        2.7
## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
## Ramon-Casas et al. 2009  0.0980 [-0.3068;  0.5028]       2.5        2.7
## Ramon-Casas et al. 2009 -0.1470 [-0.5468;  0.2528]       2.6        2.7
## Ramon-Casas et al. 2009 -0.2300 [-0.6171;  0.1571]       2.7        2.9
## Ramon-Casas et al. 2009  0.2400 [-0.1451;  0.6251]       2.8        2.9
## Ramon-Casas et al. 2009  0.4350 [ 0.1037;  0.7663]       3.7        3.7
## Hojen et al.            -0.0510 [-0.5557;  0.4537]       1.6        1.8
## Hojen et al.             0.0510 [-0.4537;  0.5557]       1.6        1.8
## Hojen et al.             0.0790 [-0.4239;  0.5819]       1.6        1.9
## Hojen et al.            -0.0790 [-0.5819;  0.4239]       1.6        1.9
## 
## Number of studies combined: k = 31
## 
##                          COR            95%-CI     z p-value
## Fixed effect model   -0.0402 [-0.1043; 0.0238] -1.23  0.2181
## Random effects model -0.0393 [-0.1127; 0.0340] -1.05  0.2931
## 
## Quantifying heterogeneity:
## tau^2 = 0.0094; H = 1.13 [1.00; 1.42]; I^2 = 22.0% [0.0%; 50.1%]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  38.45   30  0.1386
## 
## Details on meta-analytical method:
## - Inverse variance method
## - DerSimonian-Laird estimator for tau^2
## - Untransformed correlations
\end{verbatim}

@@

The main goal of this paper was to assess mispronunciation sensitivity
and its maturation with age. The results are clear: Although infants
consider a mispronunciation as a better match with the target image than
a distractor image, there was a consistent effect of mispronunciation
sensitivity. This did not change with development. Of the 3 predictions
and assumptions about the development of infants' sensitivity to
mispronunciations discussed in the Introduction, the present results
lend some support for the argument that mispronunciation sensitivity
stays consistent as infants develop. This runs counter to existing
theories of phono-lexical development, which predict either an increase
(PRIMR ref) or decrease (Assim Model ref) in mispronunciation
sensitivity.

{[}KATIE{]} CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF
SO, THIS IS THE PARAGRAPH

In sum, it seems that current theories of infants' phono-lexical
development cannot fully capture our results and should be reconsidered
with all the evidence in mind.

Alternatively, the lack of developmental change in mispronunciation
sensitivity could be due to differences in the types of tasks given to
infants of different ages. To examine this possibility, we include an
exploratory analysis of whether different moderators and experimental
design features were included at different ages, in addition to
investigating the role that these moderators play in mispronunciation
sensitivity.

@@

To understand the relationship between number of features changed and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with number of features changed as a moderator. The moderator
test was significant, QM(1) = 76.10, \emph{p} \textless{} .001. Hedges'
\emph{g} for number of features changed was -0.12 (SE = 0.01), which
indicated that as the number of features changed increased, the effect
size Hedges' \emph{g} significantly decreased (95\% CI {[}-0.15,
-0.10{]}, \emph{p} \textless{} .001). We plot this relationship in
Figure X. This confirms previous findings of a graded sensitivity to the
number of features changed for both consonant (White \& Morgan, 2008)
and vowel (Mani \& Plunkett, 2011) mispronunciations as well as the
importance of controlling for the degree of phonological mismatch in
experimental design.

@@

{[}KATIE{]} WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?

>>>>

@@

@@

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 2) or using reported
t-values (\emph{n} = 2). Raw means and standard deviations were
extracted from figures for 3 papers. In a within-participation design,
when two means are compared (i.e.~looking during pre- and post-naming)
it is necessary to obtain correlations between the two measurements at
the participant level to calculate effect sizes and effect size variance
based on t-values. Upon request we were provided with correlation values
for one paper (Altvater-Mackensen, 2010); we were able to compute
correlations using means, standard deviations, and t-values for \emph{n}
= 4 (following Csibra, et al. 2016, Appendix B; see also Rabagliati,
Ferguson, \& Lew-Williams, 2018). Correlations were imputed for the
remaining papers (see Black \& Bergmann, 2017, for the same procedure).
We could compute a total of 104 effect sizes for correct pronunciations
and 147 for mispronunciations.

@@

{[}CHRISTINA: Do you think we have to revise this section? I think it's
the same as in the proceedings paper.{]}{[}KATIE: Are you concerned
about the Publication Bias section in particular, or the Methods as a
whole? In general, some of the Methods was written before the CogSci
paper and in other places to flesh things out I rewrote what we had in
the CogSci paper. Its definitely giving the same information and
sometimes the wording is close, because there's not too many different
ways to explain what a funnel plot is :){]}

@@

{[}CHRISTINA: Let's both reread the full paper once it is ready and
check that this is properly motivated and whether we do need to list
them all. For now I think the last sentence is fine, but I would tend to
prefer a reminder for the forgetful reader.{]}{[}KATIE: that's
reasonable! We had just listed everything 7 paragraphs before, which
doesn't seem like a lot of \enquote{space}. Alternatively, this
information could be listed in a table, and then just referred to.{]}

@@

@@

@@

We first calculated the meta-analytic effect for object identification,
i.e.~looks to the target image in response to correctly pronounced
words. The variance-weighted meta-analytic effect size Hedges' \emph{g}
was 0.908 (SE = 0.12) which was significantly different from zero (95\%
CI{[}0.673, 1.143{]}, \emph{p} \textless{} .001). This is a rather large
effect size (according to the criteria set by Cohen, 1988; see also
Bergmann, et al., 2018; for comparative meta-analytic effect sizes in
language acquisition research). That the effect size is significantly
above zero suggests that when presented with the correctly pronounced
label, infants fixated the corresponding object. Our analysis of funnel
plot asymmetry, however, found evidence for publication bias, which
might lead to an overestimated effect sizes as smaller, non-significant
results might not be published. Although the effect size Hedges'
\emph{g} may be overestimated for object identification in response to
correctly pronounced words, the p-curve results and a CI lower bound of
0.67 suggests that this result is robust even when correcting for
publication bias. In other words, we are confident that the true
population mean lies above zero for object recognition of correctly
pronounced words.

{[}CHRISTINA: Can you explain what the CI lower bound means here? I
don't follow.{]}{[}KATIE: What do you think about this (last sentence)?
The CI lower bound stuff here actually comes from something you wrote,
so tell me whether its correct.{]}

We then calculated the meta-analytic effect for object identification in
response to mispronounced words. In this case, the variance-weighted
meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
was also significantly different from zero (95\% CI{[}0.133, 0.367{]},
\emph{p} \textless{} .001). This is considered a small effect size
(Cohen, 1988), but significantly above zero, which suggests that even
when presented with a mispronounced label, infants fixated the correct
object. In other words, infants are able to resolve mispronunciations, a
key skill in language processing We again note the publication bias
(which was smaller in this condition), and the possibility that the
effect size Hedges' \emph{g} may be overestimated. But, as the p-curve
indicated evidential value, we are confident in the overall patterns,
namely that infants fixate the target even after hearing a mispronounced
label.

@@

The above two analyses considered the data from mispronounced and
correctly pronounced words separately. To evaluate mispronunciation
sensitivity, we compared the effect size Hedges' \emph{g} for correct
pronunciations with mispronunciations directly, merging the two
datasets. The moderator test was significant, QM(1) = 215.761,
\emph{p}\textless{} .001. Hedges' \emph{g} for mispronunciation
sensitivity was 0.495 (SE = 0.034), which indicated that the responses
across conditions were significantly different (95\% CI{[}0.429,
0.561{]}, \emph{p} \textless{} .001). This confirms that although
infants fixate the correct object for both correct pronunciations and
mispronunciations, the observed fixations to target (as measured by the
effect sizes) were significantly greater for correct pronunciations. In
other words, we observe a significant difference between the two
conditions and can now quantify the modulation of fixation behavior in
terms of standardized effect sizes.

@@

To evaluate the different predictions we laid out in the introduction
for how mispronunciation sensitivity will change as infants develop, we
next added the moderator age (centered, in days). In the first analyses,
we investigate the impact of age separately on conditions where words
were either pronounced correctly or not. Age did not significantly
modulate object identification in response to correctly pronounced QM(1)
= 215.761, \emph{p}\textless{} .001 or mispronounce words QM(1) =
215.761, \emph{p}\textless{} .001. The lack of a significant modulation
together with the small estimates indicates that there was no
relationship between age and target looks in response to a correctly
pronounced or mispronounced label. This relationship is plotted in
Figure 2.

We then examined the interaction between age and mispronunciation
sensitivity (correct vs.~mispronounced words) in our whole dataset. The
moderator test was significant QM(1) = 215.761, \emph{p}\textless{}
.001. This result is in line with the general observation that as
infants mature they become better at language processing. The
interaction between age and mispronunciation sensitivity, however, was
not significant \(\beta\) = 0.003, SE = 0.008, 95\% CI{[}-0.012,
0.018{]}, \emph{p}= 0.731. The small estimate size, as well as
inspection of Figure 2 suggests that as infants age, their
mispronunciation sensitivity remains the same.

@@

Of the 32 papers included in the meta-analysis, 8 (comprehension = 7
papers; production = 1) analyzed the relationship between vocabulary
scores and mispronunciation sensitivity, specifically object recognition
for correct pronunciations and mispronunciations. There is reason to
believe that production data are different from comprehension data (the
former being easier to estimate for parents in the typical
questionnaire-based assessment), so we analyze this data separately.

{[}CHRISTINA{]} SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT
ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD
(LANGUAGE ETC). I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI,
NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE
SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE
SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES
NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP
SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA. {[}KATIE: Ah,
so because for each paper the correlation and CI values straddle 0, this
indicates that there really isn't much evidence for a relationship? I've
tried to write this out below, let me know what you think. Over the
summer, I had also played around with looking at how collection of
vocabulary data has dropped off over the years, even though more
mispronunciation studies have been published. That might be something
interesting to add. If we truly think that this is what is driving the
development of mispronunciation sensitivity, then why are people not
collecting this data?{]} (BUT I WONDER WHETHER WECOULD ENCODE THE
REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING
WITH THAT?) {[}KATIE: I'm not really sure what you mean by this :({]}

{[}Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page
80 as a model for writing up these results. I haven't the funniest clue
what I'm doing! :p{]}

We first considered the relationship between vocabulary and object
recognition for correct pronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 9 of 12 experimental conditions, with correlation
values ranging from -0.17 to 0.48. The mean effect size XXX was 0.0897,
but did not differ significantly from zero (95\% CI{[}-0.0105; 0.1900{]}
\emph{p} = .0795). Higher production scores were also associated with
greater object recognition in response to correct pronunciations for 9
of 16 experimental conditions, with correlation values ranging from
-0.23 to 0.44. The mean effect size XXX was 0.0601, but did not differ
significantly from zero (95\% CI{[}-0.0331; 0.1533{]} \emph{p} = .2061).
For both comprehension and production scores, the small correlation
effect sizes and large variances suggest a lack of relationship between
vocabulary and object recognition for correct pronunciations.

We next considered the relationship between vocabulary and object
recognition for mispronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 17 of 31 experimental conditions, with correlation
values ranging from -0.35 to 0.57. The mean effect size XXX was 0.0377,
but did not differ significantly from zero (95\% CI{[}-0.0260; 0.1014{]}
\emph{p} = .2465). For production, however, lower production scores were
associated with greater object recognition in response to
mispronunciations for 16 of 31 experimental conditions, with correlation
values ranging from -0.28 to 0.44. The mean effect size XXX was -0.0402,
but did not differ significantly from zero (95\% CI{[}-0.1043; 0.0238{]}
\emph{p} = .2181). For both comprehension and production scores, the
small correlation effect sizes and large variances suggest a lack of
relationship between vocabulary and object recognition for
mispronunciations.

@@

The main goal of this paper was to assess mispronunciation sensitivity
and its maturation with age. The results are clear: Although infants
consider a mispronunciation as a better match with the target image than
a distractor image, there was a consistent effect of mispronunciation
sensitivity. This did not change with development. Of the 3 predictions
and assumptions about the development of infants' sensitivity to
mispronunciations discussed in the Introduction, the present results
lend some support for the argument that mispronunciation sensitivity
stays consistent as infants develop. This runs counter to existing
theories of phono-lexical development, which predict either an increase
(PRIMR ref) or decrease (Assim Model ref) in mispronunciation
sensitivity. Furthermore, counter to the predictions for the PRIMR
(PRIMR ref) and Assimilation(Assim ref) models, we found no relationship
between vocabulary and target looking for correct pronunciations or
mispronunciations. In sum, it seems that current theories of infants'
phono-lexical development cannot fully capture our results and should be
reconsidered with all the evidence in mind.

Alternatively, the lack of developmental change in mispronunciation
sensitivity could be due to differences in the types of tasks given to
infants of different ages. In the following section, we investigate the
role that different moderators play in mispronunciation sensitivity. To
investigate the possibility of systematic differences in the tasks
across ages, we additionally include an exploratory analysis of whether
different moderators and experimental design features were included at
different ages.

@@

To understand the relationship between number of features changed and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with number of features changed as a moderator. The moderator
test was significant, QM(1) = 215.761, \emph{p}\textless{} .001. Hedges'
\emph{g} for number of features changed was -0.123 (SE = 0.014), which
indicated that as the number of features changed increased, the effect
size Hedges' \emph{g} significantly decreased (95\% CI{[}-0.151,
-0.096{]}, \emph{p} \textless{} .001). We plot this relationship in
Figure 3. This confirms previous findings of a graded sensitivity to the
number of features changed for both consonant (White \& Morgan, 2008)
and vowel (Mani \& Plunkett, 2011) mispronunciations as well as the
importance of controlling for the degree of phonological mismatch in
experimental design.

\subsection{Figure 3}\label{figure-3}

@@

{[}KATIE{]} WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO? I'M
THINKING NO
